\documentclass[draft]{article}
\usepackage{amsmath}

% new commands
\newcommand{\collaborators}[1]{\emph{Collaborators: #1}}
\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\lang}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\BPP}{\class{BPP}}
\newcommand{\NP}{\class{NP}}
\newcommand{\cid}{\overset{c}{\simeq}}
\renewcommand{\pmod}[1]{\,(\bmod{\,#1})}
\newcommand{\poly}{\textrm{poly}}
\newcommand{\getr}{\overset{R}{\gets}}
\newcommand{\getrsingle}{\getr\{0, 1\}}
\newcommand{\getrn}{\getrsingle^n}
\newcommand{\getrpoly}{\getrsingle^{poly(n)}}

% author, date, and title
\author{Jef{}frey~Finkelstein}
\date{16 February 2012}
\title{CS548 problem set 3}

\begin{document}
\maketitle
\collaborators{Dimitris, Davide, Ben}
\begin{enumerate}
\item
  We wish to show that if the basic non-interactive zero knowledge protocol of Feige and Shamir is a two-time non-interactive zero knowledge protocol, then $\lang{HAMCYCLE}\in\BPP$ and hence $\NP\subseteq\BPP$.

  In the basic non-interactive zero knowledge protocol of Feige and Shamir for \lang{HAMCYCLE}, the output of the simulator $S$ includes a pair of injective functions from the vertices of the common input graph $G$ to the rows and columns of the Hamiltonian submatrix of the common reference string.
  We construct a $\BPP$ algorithm which runs the simulator $S$ two times (simulating the prover using the same common reference string twice) to decide whether two different graphs have Hamiltonian cycles.
  We use the two pairs of injective functions which $S$ outputs to construct an isomorphism from a graph with a known Hamiltonian cycle to a subgraph of the original input graph $G$.

  Suppose the following:
  \begin{itemize}
  \item The common input for the protocol is a graph $G$ with vertex set $V$ and edge set $E$.
    Let $C_G$ be the Hamiltonian cycle in $G$ (if it exists).
  \item $C_n$ is the \emph{cycle graph} on $n$ vertices, defined by vertex set $\{1, 2, \ldots, n\}$ and edge set $\left\{(i, i \pmod{n} + 1)\,\middle|\, i\in \{1, 2, \ldots, n\}\right\}$.
  \item The prover uses the same common reference string $M$ over two instances of the protocol (with two common input graphs), and the simulator simulates this reuse as well.
  \item $H$ is the Hamiltonian submatrix of the common reference string $M$ and $C_H$ is the corresponding Hamiltonian cycle (if $H$ exists in $M$).
  \item The prover provides a certificate given by a pair of injective functions $(\pi_1, \pi_2)$, where $(u, v)\in C_G$ implies $(\pi_1(u), \pi_2(v))\in C_H$.
  \end{itemize}
  We will construct two algorithms, a helper function $A'$ and a main algorithm $A$ which uses $A'$ as a subroutine, in order to simplify our analysis later.
  Construct the function $A'$ as follows on input $G$:
  \begin{enumerate}
  \item Run $S$ on $G$ to get $T_G$, the transcript which results from the simulation, including $(\phi_1, \phi_2)$, a pair of injective functions describing a mapping from $C_G$ to $C_H$.
  \item Run $S$ on $C_n$ to get $T_{C_n}$, the transcript which results from the simulation, including $(\psi_1, \psi_2)$, a pair of injective functions describing a mapping from $C_n$ to $C_H$.
  \item Output $T_G$ and $T_{C_n}$ along with $(\Phi_1, \Phi_2)$, defined to be $(\phi_1^{-1}\circ\psi_1, \phi_2^{-1}\circ\psi_2)$.
  \end{enumerate}
  Note that the output of this function is a pair of injective functions describing a mapping from $C_n$ to $G$.
  Since $\phi_1$ and $\psi_1$ are both injective and both map $n$ vertices onto the $n$ rows of $H$, $\phi_1^{-1}\circ\psi_1$ is an injective mapping from the vertices of $C_n$ to the vertices of $G$.
  The same reasoning applies to $\phi_2^{-1}\circ\psi_2$ and the columns of $H$.
  These mappings compose (with high probability) because $S$ simulates (with high probability) the prover using the same common reference string twice.

  Construct the decision algorithm $A$ as follows on input $G$:
  \begin{enumerate}
  \item Run algorithm $A'$ on input $G$ to yield $(\Phi_1, \Phi_2)$ (ignore the rest of the transcripts).
  \item 
    Check that $(\Phi_1, \Phi_2)$ describes a Hamiltonian cycle in $G$.
    Specifically, accept if and only if
    \begin{displaymath}
      \left\{(\Phi_1(i), \Phi_2(i \pmod{n} + 1)) \,\middle|\, i \in \{1, 2, \ldots, n\}\right\}\subseteq E.
    \end{displaymath}
  \end{enumerate}

  We claim that $A$ runs in probabilistic polynomial time.
  The running time of the first two steps of $A'$ is polynomial in the size of the graph $G$ because $S$ is a probabilistic polynomial time machine.
  In the third step of $A'$, computing the images under $(\Phi_1, \Phi_2)$ of the integers $1$ through $n$ can be performed in polynomial time.
  In $A$, checking that each pair $(\Phi_1(i), \Phi_2(i \bmod{n} + 1))$ is in $E$ can be done in polynomial time.
  Since each step of the algorithm can be performed in probabilistic polynomial time and there are a constant number of steps, the algorithm $A$ runs in probabilistic polynomial time.
  It remains to bound the error probabilities of $A$.

  First suppose that $G\in\lang{HAMCYCLE}$, so $G$ has a Hamiltonian cycle.
  $C_n\in\lang{HAMCYCLE}$ as well.
  Let $(\pi_1, \pi_2)$ and $(\sigma_1, \sigma_2)$ be the pairs of injective functions describing a mapping from $C_G$ to $C_H$ and $C_n$ to $C_H$, respectively, with high probability which are output by the $(P, V)$ protocol when run with common input $G$ and $C_n$, respectively.
  Suppose $(\phi_1, \phi_2)$ and $(\psi_1, \psi_2)$ are outputs of $S$ as described in the function $A'$.
  By the zero-knowledge property of the Feige--Shamir protocol, $(\pi_1, \pi_2)\cid (\phi_1, \phi_2)$ and $(\sigma_1, \sigma_2)\cid(\psi_1, \psi_2)$.
  Now $(\pi_1^{-1}\circ\sigma_1, \pi_2^{-1}\circ\sigma_2)$ and $(\phi_1^{-1}\circ\psi_1, \phi_2^{-1}\circ\psi_2)$ are pairs of injective functions, both mapping $C_n$ to $C_G$ with high probability (and the mappings compose because they each have domain and range of size $n$), and further $(\pi_1^{-1}\circ\sigma_1, \pi_2^{-1}\circ\sigma_2) \cid (\phi_1^{-1}\circ\psi_1, \phi_2^{-1}\circ\psi_2)$.

  We want to show that $\Pr[S\text{ accepts}]\geq 1-\eta(m)$ where $\eta$ is a negligible function and $m$ is the security parameter.
  For brevity, let $X$ be the event ``$(\phi_1^{-1}\circ\psi_1, \phi_2^{-1}\circ\psi_2)$ describes a cycle in $G$'' (so $\Pr[S\text{ accepts}]=\Pr[X]$) and $Y$ be the event ``$(\pi_1^{-1}\circ\psi_1, \pi_2^{-1}\circ\psi_2)$ describes a cycle in $G$''.
  Since $X\cid Y$ by the last sentence of the previous paragraph and since $Pr[Y]\geq 1-\nu(m)$ for some negligible function $\nu$ by the completeness of the $(P, V)$ protocol, we have
  \begin{align*}
    & \left|\Pr[X] - \Pr[Y]\right| \leq \nu(m) \\
    \implies & \Pr[X] \geq \Pr[Y] - \nu(m) \\
    \implies & \Pr[X] \geq 1 - \eta(m) - \nu(m) \\
    \implies & \Pr[X] \geq 1 - (\eta(m) + \nu(m))
  \end{align*}
  where $\nu$ is some negligible function which comes from the computational indistinguishability of the events $X$ and $Y$.
  Since the sum of two negligible functions is itself a negligible function, $\Pr[X]$ is bounded below by $1-\kappa(n)$ where $\kappa(n)$ is a negligible function.
  Event $X$ occurs exactly when algorithm $A$ accepts, so $A$ accepts with high probability.

  Suppose now that $G\notin\lang{HAMCYCLE}$, so no permutation of the vertices of $G$ is a Hamiltonian cycle.
  We wish to show that algorithm $A$ accepts with low probability.
  Assume that $A$ accepts $G$ with non-negligible probability with the intention of producing a contradiction.
  If $A$ accepts $G$ with non-negligible probability it follows from the construction of $A$ that $A'$ outputs a pair $(\Phi_1, \Phi_2)$ which defines a mapping from $C_n$ to a ``cycle'' in $G$ with non-negligible probability.
  Since $(\psi_1, \psi_2)$ describes a mapping from $C_n$ to $C_H$ correctly with high probability (because $C_n\in\lang{HAMPATH}$), the faulty part of this mapping is $(\phi_1^{-1}, \phi_2^{-1})$.
  Hence $(\phi_1, \phi_2)$ is the certificate which will cause the verifier to accept with non-negligible probability.

  We will construct a cheating prover which uses $A'$ to fool $V$ into accepting $G$ with non-negligible probability.
  The prover proceeds as follows on input $G$:
  \begin{enumerate}
  \item
    Run $A'$ to produce $T_G$, $T_{C_n}$, and $(\Phi_1, \Phi_2)$.
  \item Forward the appropriate parts of $T_G$ to the verifier.
  \end{enumerate}
  Running the $(P, V)$ protocol with this cheating prover on input $G$ will cause the prover to send the certificate $(\phi_1, \phi_2)$.
  As stated in the previous paragraph, the verifier will accept this string with non-negligible probability.

\item
  \begin{enumerate}
  \item
    Let $(Gen, Enc, Dec)$ be the CPA-secure encryption scheme with no decryption error and $(P, V)$ be the one-time adaptive non-interactive zero knowledge protocol, both as described in the problem.
    Let $(P_R, V_R)$ be the protocol constructed using the encryption scheme and the $(P, V)$ protocol.
    We must show completeness, soundness, the zero knowledge property, and the proof of knowledge property.
    \begin{description}
    \item[Completeness] \hfill \\
      Suppose $x$ is in the language induced by the $\NP$ relation $R$, so there exists a $w$ with length polynomial in the length of $x$ such that $(x,w)\in R$.
      $V_R$ accepts when interacting with $P_R$ if the simulated $(P, V)$ interaction accepts.
      By the completeness property of the underlying $(P, V)$ protocol, $V$ accepts on common input $(x, e, c)$, common reference string $r$, and certificate sent by the prover $p$ with high probability if $((x, e, c), (w, \rho))\in R'$.
      Since for an honest prover and verifier $((x, e, c), (w, \rho))\in R'$, it follows that $V$ will accept with high probability and hence $V_R$ will also.
    \item[Soundness] \hfill \\
      The proof is by contradiction, reducing from the soundness of the underlying protocol.
      Assume with the intention of producing a contradiction that the protocol $(P_R, V_R)$ is not computationally sound, so there exists a cheating prover $P^*_R$ such that for all $x\notin L_R$,
      \begin{displaymath}
        \Pr\left[r\getr\{0,1\}^{\poly(n)}, (x, p)\gets P^*_R(r); V_R(x, r, p)=1\right]>\eta(n),
      \end{displaymath}
      for all negligible functions $\eta$.
      Construct cheating prover $P^*$ as follows on common reference string $r$:
      \begin{itemize}
      \item Choose $x\getrn$ and $e\getrpoly$.
      \item Run $P^*_R$ on common input $x$ and common reference string $e\circ r$ to yield $(c, p)$.
      \item Send to $V$ the (generated) common input $(x, e, c)$ and certificate $p$.
      \end{itemize}

      By the construction of $V$, $V$ accepts on common input $x$ and common reference string $e\circ r$ if and only if $V_R$ accepts on common input $(x,e,c)$ and common reference string $r$.
      Therefore,
      \small{%
         \begin{align*}%
         & \Pr\left[r\getrpoly, ((x, e, c), p)\gets P^*(r); V((x, e, c), r, p)=1\right] \\
         = & \Pr\left[e\circ r\getrpoly, (c, p)\gets P^*_R(r, x); V_R((x, e, c), r, p)=1\right],
       \end{align*}%
      }%
      which is greater than negligible, from above.
      This is a contradiction with the hypothesis that $(P, V)$ is a sound proof system.
      Therefore $(P_R, V_R)$ is sound.
    \item[Zero knowledge] \hfill \\
      We will show that since $(P, V)$ is an adaptive zero-knowledge protocol, $(P_R, V_R)$ is an adaptive zero-knowledge protocol, which implies $(P_R, V_R)$ is a non-adaptive zero-knowledge protocol.
      Let $S$ be the adaptive simulator for the $(P, V)$ protocol.
      Construct $S_R$, the adaptive simulator for the $(P_R, V_R)$ protocol, which proceeds as follows on input $1^n$:
      \begin{enumerate}
      \item Choose $e\getrpoly$ and $\rho\getrpoly$.
      \item Run $S(1^n)$ to yield $r$.
      \item Send $e\circ r$ to the verifier.
      \item
        Receive $(x, w)$ from the verifier.
        Let $c=Enc_e(w, \rho)$.
      \item Provide $(x, e, c)$ to $S$, which yields $p$.
      \item Send $(c, p)$ to the verifier.
      \end{enumerate}
      We claim that for all adversarial verifiers $V_R^*$, the verifier cannot distinguish between interacting with the prover $P_R$ and interacting with the simulator $S_R$.
    \item[Proof of knowledge] \hfill \\
      Let $P_R^*$ be a cheating prover for the $(P_R, V_R)$ protocol.
      Construct extractor $E$ as follows on input $x$ and auxiliary input $z$:
      \begin{enumerate}
      \item Run $G(1^n)$ to yield encryption key $e$ and decryption key $d$.
      \item Choose $r\getrpoly$.
      \item
        Run $P_R^*$ on input $x$, auxiliary input $z$, and common reference string $e\circ r$.
        It outputs $c$ and $p$.
      \item Let $w=Dec_d(c)$, where $D_d$ is the decryption algorithm with decryption key $d$.
      \item Output $(e\circ r, (c, p), w)$.
      \end{enumerate}
      We claim this extractor satisfies the two properties for a proof of knowledge extractor.

      First, since $E$ chooses $e\circ r$ randomly and provides them directly to $P^*$, and since $E$ simply outputs $(c, p)$, the result of running $P_R^*$ on input $x$, $z$, and $e\circ r$, we have
      \begin{displaymath}
        (e\circ r, (c, p))\cid [r\getrpoly, (c, p)=P_R^*(x, e\circ r, z); (e\circ r, (c, p))].
      \end{displaymath}
      Second, we need either $\Pr[V(x, e\circ r, (c, p))]$ or $\Pr[(x, w)\in R]$ to be at most negligible in $n$, which implies that the intersection of these two events is negligible in $n$.
      In the case that the prover $P_R^*$ is an honest prover, then the latter probability will be negligible, since the witness $w$ is the error-less decryption of $c$, so the probability that $(x, w)\notin R$ is negligible.
      In the case that the prover $P_R^*$ is a cheating prover, then the former probability will be negligible, since the probability that $V(x, e\circ r, (c, p))$ accepts is negligible by the soundness of the $(P_R, V_R)$ protocol.

      We have shown that this extractor satisfies the two conditions necessary for the proof of knowledge property.
    \end{description}
  \item
    Let $(G, E, D)$ be a CPA-secure encryption scheme with no decryption error.
    Construct a new encryption scheme $(G, E, D')$ where $D'$ is defined as
    \begin{displaymath}
      D'_d(c)=
      \begin{cases}
        \bot & \text{if } D_d(c) = x \\
        D_d(c) & \text{otherwise}
      \end{cases}
    \end{displaymath}
    where $x$ is a single fixed string.
    This is still CPA-secure (if not, we could break the underlying CPA-secure encryption scheme with non-negligible probability), but now the probability of a bad decryption of strings of length $n=|x|$ is $\frac{1}{2^n}$, which is negligible.
    There now exists an $x$ such that if $(e\circ r, (c, p), w)\gets E(x, z)$, then $\Pr[V(x, e\circ r, (c, p))=1 \land (x, w)\notin R]$ is non-negligible.
    This is because $(x, w)\notin R$ with non-negligible probability (since $w=\bot$) but $V$ still would have accepted $(x, e\circ r, (c, p))$ with high probability.
    This violates the second condition for the proof of knowledge property, so the $(P_R, V_R)$ protocol is not a proof of knowledge.
  \end{enumerate}
\item
  The proof is by contradiction using a hybrid argument.
  Assume $(P, V)$ is not a $k$-proof adaptive non-interactive witness indistinguishable protocol.
  Therefore there exists a probabilistic polynomial time verifier $V^*$, an auxiliary input $z$, a negligible function $\eta$, and a sufficiently large $n$ such that $\Pr[b=b'] > \frac{1}{2} + \eta(n)$.
  Suppose each iteration of the loop in the game is numbered from $1$ up to $k$.
  Define experiment $exp\mbox{-}k$ the instance of the game in which $b=1$ and $exp\mbox{-}0$ the instance of the game in which $b=0$.
  Construct intermediate hybrid experiments $exp\mbox{-}i$ in which the prover receives $w_0$ in each round up to and including round $i$ and $w_1$ in each round after round $i$, where $i\in\{0, 1, \ldots, k\}$.
  (Note that when $i=0$, $exp\mbox{-}i$ corresponds to an instance of the game in which $b$ was chosen to be $0$, and when $i=k$, $exp\mbox{-}i$ corresponds to an instance of the game in which $b$ was chosen to be $1$.)

  By a standard averaging argument, there exists an $i\in\{0,1,\ldots, k-1\}$ such that
  \begin{displaymath}
    \left|\Pr\left[V^*\text{ accepts in } exp\mbox{-}i\right] - \Pr\left[V^*\text{ accepts in } exp\mbox{-}(i+1)\right]\right| > \frac{\eta(n)}{k}.
  \end{displaymath}
  The only difference between $exp\mbox{-}i$ and $exp\mbox{-}(i+1)$ is that in round $i$, $V^*$ receives the output of $P(x, r, w_0)$ in the former and the output of $P(x, r, w_1)$ in the latter.

  Construct non-uniform cheating verifier $\tilde{V}$ which will break the 1-round game as follows on auxiliary input $i$:
  \begin{enumerate}
  \item Receive $r\getr\{0,1\}^{poly(n)}$ and $b\getr\{0, 1\}$.
  \item Simulate the interaction of the $k$-round verifier $V^*$ and the $k$-round prover $P$ with initial randomness $r$ and bit $0$ for $i - 1$ rounds.
  \item On the $i$th round, give $r$ and $b$ to $V^*$, which yields $(x, w_0, w_1)$.
  \item Forward $(x, w_0, w_1)$ to the external 1-round prover $P$, which yields $p=P(x, r, w_b)$.
  \item Forward $p$ to the internal $k$-round verifier $V^*$.
  \item Simulate the interaction of $V^*$ and $P$ with initial randomness $r$ and bit $1$ for the remaining $k - i$ rounds.
  \item Output whatever bit $V^*$ outputs after $k$ rounds.
  \end{enumerate}

  Now we have
  \begin{align*}
    & \left|\Pr\left[\tilde{V} \text{ wins} \,\middle|\, b=0\right] - \Pr\left[\tilde{V} \text{ wins} \,\middle|\, b=1\right]\right| \\
    = & \left|\Pr\left[V^*\text{ accepts in } exp\mbox{-}i\right] - \Pr\left[V^*\text{ accepts in } exp\mbox{-}(i+1)\right]\right| > \frac{\eta(n)}{k}.
  \end{align*}
  This is equivalent to $\Pr[\tilde{V}\text{ outputs } b' \text{ such that } b'=b] > \frac{\eta(k)}{n}$.
  Since $\frac{\eta(k)}{n}$ is a negligible function, $V^*$ can distinguish whether $P$ knows $w_0$ or $w_1$.
  This is a contradiction with the hypothesis that $(P, V)$ is a $1$-proof adaptive non-interactive witness indistinguishable protocol.
  Therefore we conclude that $(P, V)$ is a $k$-proof adaptive non-interactive witness indistinguishable protocol.
\end{enumerate}
\end{document}
