\documentclass[draft]{article}
%\usepackage{fullpage}
%\usepackage{amsmath}
\usepackage{amssymb}

% new commands
\newcommand{\collaborators}[1]{\emph{Collaborators: #1}}
%\newcommand{\cid}{\overset{c}{\simeq}}
%\newcommand{\ncid}{\overset{c}{\not\simeq}}
%% \newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
%\newcommand{\getr}{\overset{R}{\gets}}
%\newcommand{\getrn}{\getr\{0, 1\}^n}
%\newcommand{\getrsingle}{\getr\{0, 1\}}
%% \newcommand{\getrell}{\getr\{0, 1\}^{\ell(n)}}
%\newcommand{\getrpoly}{\getrsingle^{poly(n)}}
%% \newcommand{\NP}{\class{NP}}
%\newcommand{\mim}{\mathsf{mim}}
%\newcommand{\msim}{\mathsf{sim}}

% author, date, and title
\author{Jef{}frey~Finkelstein}
\date{1 May 2012}
\title{CS548 problem set 7}

\begin{document}
\maketitle
\collaborators{Ben, Davide, Dimitris}
\begin{enumerate}
\item
  Proof by contrapositive.
  Assume $\pi$ does not securely emulate $\phi$, so there exists an adversary $A'$ such that for all simulators $S'$ there exists an environment $E'$ and some auxiliary information $z'\in\{0, 1\}^n$ such that the two probability ensembles are computationally distinguishable, for some $n\in\mathbb{N}$.
  Our goal is to show that there exists an adversary $A$ and an environment $E$ such that for all simulators $S$ there exists an auxiliary input $z$ such that the two probability ensembles are computationally distinguishable, for some $n'\in\mathbb{N}$.
  Choose $A=A'$.
  Construct environment $E$ which, on auxiliary input $z=(E', z')$, does exactly what $E'(z')$ does.
  The $E'$ and $z'$ included in the auxiliary input $z$ are the environment and auxiliary input which correspond to the external simulator $S$ with which $E$ will be interacting (in the ideal interaction).
  We know such an $E'$ and $z'$ exist by our initial assumption (that is, for all $S'$ there exist an $E'$ and $z'$, etc.; in this case, $S$ is covered by the universally quantified $S'$).

  Since we chose $A=A'$ and $E'$ and $z'$ to depend on the external simulator $S$, the output of $E(z)$ will be distributed identically to the output of $E'(z')$ in both the real and ideal interactions.
  Since the $(E', \pi, A')$ and $(E', \phi, S)$ probability ensembles are computationally distinguishable with auxiliary input $z'$, so will be the $(E, \pi, A)$ and $(E, \phi, S)$ with auxiliary input $z=(E', z')$.
\item
  \begin{enumerate}
  \item $\mathcal{F}_{OT}$ is defined as follows:
    \begin{enumerate}
    \item Receive $x_0$ and $x_1$ from sender.
    \item Receive $b$ from receiver.
    \item Send $x_b$ to receiver.
    \end{enumerate}
  \item I don't know.
  \item I don't know.
  \end{enumerate}
\item
  \begin{enumerate}
  \item I don't know.
  \item I don't know.
  \end{enumerate}
\end{enumerate}
\end{document}
